\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-05 paper_final.tex

\section{Teaching Dimension for unknown $\eta$ and $w_0$}
Here we present an algorithm that teaches the desired concept to the Perceptron learner when we know neither the learning rate, nor the initial weight vector of
our perceptron learner.

\subsection{$\epsilon$-Bounding the angle of $w_0$}
Our algorithm will only consider the decision boundary and the weight vector of
the Perceptron in two dimensions. In other words, we are considering the plane
defined by

In order to proceed, we must define an operation that creates an
$\epsilon$-Bound around the angle of $w_o$ in the plane. It works by iteratively
partitioning the plane with unlabeled examples. For convenience, let $(a,b)$
denote a point in said plane. Let $ang(x,y)$ denote the angle between $x$ and
$y$.

@@

Assume $\exists b, \eta_{min}, \eta_{max} \in \mathbb{R}$ such that $\lVert w_0
\rVert \leq b < \infty$ and $0 < \eta_{\min} \leq \eta \leq \eta_{\max} <
\infty$.

Now that we have a bound around $\eta$, we get to the main result.
\\
\\
\textbf{Theorem 4.} 
\textit{With unknown $w_0$ such that $\lVert w_0 \rVert \leq b < \infty$
and unknown $\eta$ such that $0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ then 
$
\mathbb{T}_\epsilon(w^* , \learn) \leq 3 + T_{\text{bound}}(2\epsilon \eta_{\max})
$
where $T_{\text{bound}}(2\epsilon \eta_{\max})$ is the worst case number of examples needed to bound $\eta \in [\alpha , \beta]$ s.t. $\beta - \alpha \leq 2\epsilon \eta_{\max}$
}
\\
\\
\textit{Proof.}
First bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$

>>>>

\section{Discussions of the teaching dimension for unknown $\eta$ and $w_0$}

We present an algorithm that teaches the desired concept to the Perceptron
learner when we know neither the learning rate, nor the initial weight vector of
our perceptron learner. The algorithm works well in general, but there is a very
unlikely case that will cause the number of unsupervised queries to diverge to
infinity. We also discuss a potential problem in the definition of the teaching
dimension and prove an upper bound on the teaching dimension in this setting
given an optimal algorithm for bounding $\eta$.

\subsection{$\epsilon$-Bounding the angle of $w_0$}
Our algorithm will only consider the decision boundary and the weight vector of
the Perceptron in two dimensions. In other words, we are considering the plane

defined by,
\[
  \begin{bmatrix}
    a & b & 0 & \cdots & 0
  \end{bmatrix} ^ \top
  \textnormal{where}
  \ a, b \in \mathbb{R}
\]
The decision boundary of the Perceptron passes through the origin, so it will
also pass through the origin of this plane and create a linear decision
boundary.
\\

In order to proceed, we must define an operation that creates an
$\epsilon$-Bound around the angle of $w_o$ in the plane. It works by iteratively
partitioning the plane with unlabeled examples. For convenience, let $(a,b)$
denote a point in said plane. Let $ang(x,y)$ denote the angle between $x$ and
$y$. Let $mid(x, y)$ be the midpoint between $x$ and $y$ on the unit circle
($x$ and $y$ have the same magnitude). Let $test(\alpha)$ be an unsupervised
check of $\alpha$.

\begin{algorithm}
\caption{Bounding the angle of $w_0$}
\begin{algorithmic}[1]
	\REQUIRE $\epsilon$
  \STATE Compute $test((0,1))$, $test((1,0))$, and $test((0,-1))$

  \COMMENT{One of these will be different from the others, or $w_0 \in
  \{(1,0), (-1,0)\}$, in which case we're done.}
  \STATE $\alpha \leftarrow $ the different one, $\beta \leftarrow $ the one
  next to $\alpha$.
  \FOR{$i \leftarrow \frac{1}{4}$; $i > \epsilon$; $ i \leftarrow \frac{i}{2}$}
  \IF{$test(mid(\alpha,\beta)) \ != test(\alpha)$}
  \STATE $\beta \leftarrow mid(\alpha, \beta)$
  \ELSE
  \STATE $\alpha \leftarrow mid(\alpha, \beta)$
  \ENDIF
  \ENDFOR
  \RETURN $\alpha$, $\beta$

\end{algorithmic}
\end{algorithm}

This gets us a bound around the angle of $w_0$ in time $\ceil{log(\frac{1}{\epsilon})} +
1$.

@@

Now that we know that we can move and bound the angle of $w_0$, we can bound
$\eta$. The algorithm works by giving the perceptron a ``large enough'' update,
two times. Because the update is vector addition, the size of the update is a
linear combination of $\eta$ and $\lVert w_0 \rVert$. With two equations and two
unknowns, we can derive both $\eta$ and $\lVert w_0 \rVert$. Using basic trig,
we get,

\[
  \begin{cases}
    \lVert w_0 \rVert * \tan(\theta_1) + \eta * \lVert x \rVert (\tan(\theta_1)  
    \cos{\phi} - \sin{\phi}) = 0 \\

    \lVert w_0 \rVert * \tan(\theta_2) + \eta * 2 \lVert x \rVert (\tan(\theta_2)
    \cos{\phi} - \sin{\phi}) = 0 \\
  \end{cases}
\]
\textit{where $\theta_1, \theta_2$ are the angles of the updated $w$'s with
  $w_0$, $\phi$ is the angle of the training case with $w_0$, and $x$ is our
  training example.}

\begin{algorithm}
\caption{Bounding $\eta$}
\begin{algorithmic}[1]
	\REQUIRE $\epsilon'$: desired bound around the concept $w^*$
  \STATE $\alpha_1, \beta,_1 \leftarrow$ bounds around $w_0$ such that $w^*$ is not
  inside it

  \COMMENT{If we detect that $ang(\alpha_1, \beta_1) < \epsilon'$, we can quit the
    whole teaching procedure because the learner knows the concept.}
  \STATE $x' \leftarrow $ the most perpendicular vector to $mid(\alpha_1, \beta_1)$
  that causes an update
  \STATE $v \leftarrow$ constant ``large enough'' to make the perceptron update
  \STATE $teach(x' * v)$
  \STATE $\alpha_2, \beta_2 \leftarrow$ ``small enough'' bound around $w$
  \STATE $teach(x' * v)$
  \STATE $\alpha_3, \beta_3 \leftarrow$ ``small enough'' bound around $w$
  \STATE Solve the linear equation defined above 8 times using every combination of
  $\alpha$ and $\beta$. The $\epsilon$-Bound is the worst case of these.
\end{algorithmic}
\end{algorithm}

The problem with this algorithm appear in step 3; it is possible to come up with
concrete definitions for Steps 2, 5, 7. We can construct a case where
$\alpha_1$ and $\beta_1$ are as close as possible, without being $ < \epsilon'$,
and $w^*$ is arbitrarily close to $\alpha$. This situation can require
arbitrarily tight bounds on the angle of $w_0$, requiring arbitrarily many
unsupervised queries.
\subsection{Discussions of the Definition of Teaching Dimension}
Given that the algorithm works well in general, but diverges in certain pathological
cases, we suggest that an extension of the concept of the teaching dimension
could be useful for dealing with Machine Teaching in more complex settings.
Instead of Minmaxing the number of examples, we propose that the expected value
of a teaching algorithm is a more interesting metric. There is a parallel to
statistical learning theory: instead of using the ``minimax
rule'' to minimize the Risk, it is better to minimize the expected Risk.

\subsection{Main Result}
\textbf{Theorem 4.} 
\textit{With unknown $w_0$ such that $\lVert w_0 \rVert \leq b < \infty$
and unknown $\eta$ such that $0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ then 
$
\mathbb{T}_\epsilon(w^* , \learn) \leq 3 + T_{\text{bound}}(2\epsilon \eta_{\max})
$
where $T_{\text{bound}}(2\epsilon \eta_{\max})$ is the worst case number of examples needed to bound $\eta \in [\alpha , \beta]$ s.t. $\beta - \alpha \leq 2\epsilon \eta_{\max}$
}
\\
\\
\textit{Proof.}

First bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
